Supplementary Information

### 2020-09-01 doc/manuscript/MEE_manuscript.Rmd
add NE pubs

---
title: ''
output: word_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

>>>>

---
title: ''
output: word_document
bibliography: references.bib
csl: methods-in-ecology-and-evolution.csl
nocite: | 
  @vlam_temperature_2014; @maxwell_declining_2016; @sniderhan_growth_2016; @tumajer_increasing_2017; @alfaro-sanchez_growth_2017; @helcoski_growing_2019; @aus_de_ar_tree_2018; @bumann_assessing_2019
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
